Lyman-alpha spectra from rotating outflows

### 2018-03-27 paper/paper.tex
edit

\cite{Garavito14} presented an analytical model that
accounts for the effects of pure rotation on the
\lya\ lines 'morphology. 
The basic assumption of their analytical model is that each
differential surface element on the sphere Doppler shifts the photons
that it emits

In this paper we introduce this ansatz by post-processing the results
of the outflows simulations without rotation.
We introduce a Doppler shift as follows
\begin{equation}
x' = x + \frac{\vec{v}_{\rm rot}\cdot\hat{k}}{v_{\rm th}}
\label{eq:shift_x}
\end{equation}
%
where $x'$ is the photon's new frequency, $x$ is the photon's
frequency after being procesed by the outflow, $v_{\rm rot}$ is the 
rotational velocity at the point of escape of the photon, $\hat{k}$ is
the photon's direction of propagation and $v_{\rm th}$ is the thermal
velocity of the sphere.

@@

>>>>

\cite{Garavito14} presented an analytical model that
accounts for the effects of pure rotation on the
\lya\ line morphology. 
The basic assumption of their analytical model is that each
differential surface element on the sphere Doppler shifts the photons
that it emits.
In this paper we introduce this ansatz by post-processing the results
of the outflows simulations without rotation.
The frequency of each photon is Doppler shifted as follows

\begin{equation}
x' = x + \frac{\vec{v}_{\rm rot}\cdot\hat{k}}{v_{\rm th}}
\label{eq:shift_x}
\end{equation}
%
where $x'$ is the photon's new frequency, $x$ is the photon's
frequency after being procesed by the outflow, $v_{\rm rot}$ is the 
rotational velocity at the point of escape of the photon, $\hat{k}$ is
the photon's direction of propagation and $v_{\rm th}$ is the thermal
velocity of the sphere.

@@

Figure \ref{fig:doppler_shift} summarizes the most important trends of
our simulations.
